Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-20 manuscript/manuscript.Rmd
updated interactions
new stats section for QBM

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in

@@

#### Vital rate models: quadrat level
At the quadrat level we defined three vital rates:

>>>>

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
mainfont: times
geometry: margin=1in

@@

#### Vital rate models: quadrat level
The statistical approach used to model vital rates using aggregated data depends on the type of data collected. In our case, and as is often the case with census data, we have percent cover data (which can easily be transformed to proportion data, of course). We first considered fitting three vital rate models analagous to those we fit at the individual level: one for probability of extirpation within a quadrat (analagous to survival), one for cover change within a quadrat (analagous to growth), and one for probability of colonization within a quadrat (analagous to recruitment). However, within-quadrat extirpation and colonization events were rare in our time series (N=X and N=X, respectively). Given the broad spatial distribution of the quadrats we are studying, it is safe to assume that these events are in fact rare enough to be ignored for our purposes. So we constrained our statistical modeling of vital rates at the population level to change in percent cover within quadrats. For most of the remaining discussion of statistical modeling we refer to proportion data, which is simply percent data divided by 100.

An obvious choice for fitting a linear model to proportion data is beta regression because the support of the beta distribution is [0,1], not including true zeros. However, when we used fitted model parameters from a beta regression in quadrat-based population model the simulated population tended toward 100% cover for all species. We therefore chose a more-constrained modeling approach based on a truncated log-normal likelihood. The model is

\begin{align}
x_{jq,t+1} &= \gamma^{G}_{j,t} + \phi^{G}_{jQ} + \beta^{G}_{j,t}x_{jq,t} + \theta^{S}_{jk}C_{k,t} \\
Y^{G}_{jq,t+1} &\sim \text{LogNormal}(x_{jq,t+1}, \tau{j}) T(0,1)
\end{align}

At the quadrat level we defined three vital rates:
